Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data

### 2024-11-22 paper/paper.qmd
Revise introduction

---
title: "Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data"
author: 
  - Yunkai Gu, Anqi Xu, Yitong Wang
thanks: "Code and data are available at: https://github.com/Anjojoo/State-Level-Respondent-Estimates."
date: today
date-format: long
abstract: "This study analyzes state-level respondent estimates using data from the 2022 American Community Survey (ACS) accessed via IPUMS, and focuses on individuals with doctoral degrees and employs the ratio estimator approach to predict total respondents in each state, using California as a reference point. The results reveal discrepancies between estimates and actual figures, highlighting the limitations of assuming uniform ratios across states. These differences are attributed to variations in demographics, educational policies, and economic conditions. The analysis underscores the utility of statistical methods like ratio estimators for scalable estimates while emphasizing the importance of accounting for regional variations in such analyses."
format: pdf
number-sections: true
toc: true
---

@@

This paper utilizes the 2022 American Community Survey (ACS) data from IPUMS to explore educational attainment across states, focusing on respondents with doctoral degrees. The task involves determining the number of respondents with a doctoral degree in each state (STATEICP) and applying the ratio estimator approach of Laplace. Using California as a benchmark, where the total number of respondents across all education levels is known, the ratio of doctoral degree holders to total respondents is calculated. This ratio is then applied to other states to estimate their total respondent counts. The analysis includes a comparison of these estimates with actual state-level respondent numbers, highlighting differences and discussing potential causes for discrepancies.

@@

The analyses presented in this paper were conducted using R programming language [@citeR]. The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand. After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse]. We use `testthat` package [@citetest] to develop the test for structure and format of simulation and analysis data. Tables were constructed with `knitr` package [@citeknitr] and `tibble` package [@citetibble].

>>>>

---
title: "Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data"
author: 
  - Yunkai Gu, Anqi Xu, Yitong Wang
thanks: "Code and data are available at: https://github.com/Anjojoo/State-Level-Respondent-Estimates."
date: today
date-format: long
abstract: "This study analyzes state-level respondent estimates using data from the 2022 American Community Survey (ACS) accessed via IPUMS, and focuses on individuals with doctoral degrees and employs the ratio estimator approach to predict total respondents in each state, using California as a reference point. The results reveal discrepancies between estimates and actual figures, highlighting the limitations of assuming uniform ratios across states. These differences are attributed to variations in demographics, educational policies, and economic conditions. The analysis underscores the utility of statistical methods like ratio estimators for scalable estimates while emphasizing the importance of accounting for regional variations in such analyses."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Understanding the distribution of educational attainment across states is essential for policymakers, educators, and researchers. This study leverages data from the 2022 American Community Survey (ACS), accessed via IPUMS, to investigate state-level educational patterns, specifically focusing on individuals whose highest degree is a doctorate. While previous studies often rely on direct population counts, this work introduces a statistical perspective by employing the ratio estimator approach, a technique designed to derive population estimates using auxiliary variables.

The study aims to fill a gap in scalable population estimation by testing the applicability of a California-based ratio to other states. California, with its large population and diverse demographics, serves as the benchmark for calculating the proportion of doctoral degree holders to the total respondents. This ratio is then applied to other states to estimate their total number of respondents, allowing for an evaluation of how well such statistical models generalize across varied geographic and demographic contexts.

Results show significant discrepancies between estimated and actual respondent counts in many states, highlighting limitations in assuming uniform ratios. Factors such as state-specific demographics, educational policies, and local economies contribute to these variations. By identifying these differences, the study underscores the importance of incorporating regional nuances into statistical models for more accurate population estimates.

@@

The analyses presented in this paper were conducted using R programming language [@citeR]. The `tidyverse` packages [@citetidyverse] were used in the process of data simulation, testing beforehand. After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], data cleaning process was done by using `tidyverse` package [@citetidyverse]. We also use `tidyverse` package [@citetidyverse] to develop the test for structure and format of simulation and analysis data. Tables were constructed with `knitr` package [@citeknitr] and `tibble` package [@citetibble].
